%How did Google Glass come about? History!
%Mobiles today are used as a nervous tick. It is a distraction and something that pulls your attention away from the real world. At least that is what Sergey Brin, one of the founders of Google, claimed during a Ted Talk presentation in February 2013.\cite{tedtalkWhyGlass} Brin stated that if he was a smoker he would probably light a cigarette at those times when he now uses his phone.
%\url{http://www.ted.com/talks/sergey_brin_why_google_glass}
%
%Brin and his team wanted to create something that would make interaction with technology easy and fast and not distract from reality. They wanted to keep the information more handy and close by than a phone stuck in the users pocket. But they also wanted to keep the line of sight free. Thad Starner, technical lead/manager on Google Glass, wrote in an article in 2013,\cite{6504855} that he sought out to build something as intuitive as a watch. An extension of the self, as he stated. And so Google started working on Project Glass. 
%
%
%
%
% The idea behind Glass was to minimise the time between intention and action
% users should not have to bring up something from their pockets each time they want to interact with technology
% they should be able to just simply interact
% They wanted to create something as intuitive as a watch. 
% checking the watch is something a user might do without actually thinking about what the time is.
% they might have to check again if someone were to ask them what the time is.
% Glass should be an extension of the self rather than another device.
% // Thad Starner - technical lead/manager on Google Glass
%
% Sergey Brin, one of the founders at Google, has similar ideas
% ted talk he spoke about how checking the phone was something he did without reason
% putting notifications more easily accessible would minimise interaction with technology because the user
% would not have to check if any updates have come in, they would know right away
%
%
On April 4th, 2012, Google announced ``Project Glass''~\cite{GoogleGlassConcept}. Google Glass, as the device is now known, was under development for several years at Google's research and development department, Google X. As part of the announcement Google stated:  ``We think technology should work for you---to be there when you need it and get out of your way when you don't.''~\cite{GoogleGlassAnnouncement}.

Sergey Brin, one of the founders of Google, gave a Ted Talk in February, 2013,~\cite{tedtalkWhyGlass} where he talked about why Google decided to develop Google Glass. His argument was that users stayed on their smartphones for too long. Brin also argued that when users were using their smartphones they were looking down at a screen and were not aware of their surroundings. Instead Google wanted to create a device that would give the user notifications that could quickly be dealt and done with. Google also wanted to make the device hands-free and put the display where the user did not have to look down. Brin stated that the development team at Google X added a camera later on in the development process but in fact the camera had been a great addition to Google Glass and enabled the device to capture the user's surroundings, for instance by taking photographs.

Thad Starner, technical lead/manager (responsible for both the technical direction as well as people management~\cite{techLeadManager}) on Google Glass, claimed that Google Glass was intended to be an extension of the self~\cite{6504855}. He compared Google Glass to a watch. Not in terms of where the user keeps his or her focus (with a watch you must look down, similar to a smartphone), but rather in terms of how a watch is easy to access and how the access is instant. Starner said that with Google Glass, Google wanted to minimise the time between intention and action. 
%
\subsection{What is Google Glass?}
\label{subsec:googleglass}
\input{chap2/GlassDef.tex}
%
\subsection{User Interface}
\label{subsec:userinterface}
\input{chap2/GlassUI.tex}
%
\subsection{Similar Products}
\label{subsec:similarproducts}
\input{chap2/SimilarProducts.tex}
%
\subsection{A Comparison with Smartphones}
\label{comparedtophones}
\input{chap2/vsphones.tex}
%
\subsection{Limitations of Google Glass}
\label{subsec:limitations}
\input{chap2/Limitations.tex}
%
\subsection{QR Code}
\label{subsec:qrcode}
\input{chap2/QRCode.tex}
%
\subsection{Information (and Ways of Presenting Information)}
\label{subsec:information}
\input{chap2/Information.tex}
%
\newpage
\subsection{Summary}
\label{subsec:summary}
\input{chap2/Summary.tex}
%
%\subsection{Working handsfree}
%\label{subsec:workinghandsfree}
%Why?
%Multitasking (is this background or discussion?)
%Studies?
%\url{http://www.theguardian.com/science/2015/jan/18/modern-world-bad-for-brain-daniel-j-levitin-organized-mind-information-overload}
%\subsection{Multitasking on Google Glass}
%\label{subsec:multitaskingongoogleglass}