%o   Conclusion
%o   Project Evaluation
%o   Problems - How would you do this the next time?
%o   Future work
As seen in the test results the Google Glass application was almost always the slowest in all of the tests. However, as the test results only shows the time from when the QR code has been scanned until when the information is being displayed on screen does not differ by more then about half a second between Google Glass and Samsung Galaxy SII, and the difference in time might not be of significance. 

After the user has scanned a QR code and the information is displayed, that is when the actual usage of the application starts. A user might be able to look past the fact that the Google Glass application is slower at scanning and presenting information as the advantages of Google Glass lies not in the speed of the device but rather in the user interface.

The fact that users do not have be use their hands is the major advantage of using Google Glass over a smartphone. Although voice commands are possible to implement in the smartphone application as well, the user must still hold the smartphone or place the smartphone on a surface in order to see the information being displayed. Google Glass puts the display in front of the user and does not require the user to hold the display in any way.

However, the fact that Google Glass was not able to scan more complex QR codes is definitely a negative aspect. Although the product ID:s used in this test were not long enough as to where complexity would become an issue, the complexity of the QR code will be an issue when the database contains many, many more products and the product ID:s are such that the complexity of the QR code is too high for Google Glass to handle.

As such, one clear improvement Google must make to Google Glass is to upgrade the camera. Not only to be able to compete with smartphone cameras, which, as seen, were much better already at the time of Google Glass' release, but simply to be able to identify QR codes with higher complexity and at longer distances.

Another important aspect of Google Glass is the amount of information the device can display on one screen. As shown in the text length test, a card on Google Glass which only displays text can hold somewhere between 200 and 220 characters, in comparison to smartphones with similar layout design, which can hold somewhere between 550 and 750 characters.

According to Google's guidelines for writing text for Google Glass, the text should be brief and simple, with the most important part of the text first and without repetition. Clearly, with the limit in text length, writing short and precise text is important on Google Glass. Displaying information to the user without having to divide text up on several cards is important, for instance when writing instructions. Depending on the user to scroll back and forth between cards in order to read one instruction would not be good design, even though scrolling back and forth can be done via voice commands, and as such instructions should be simple and brief, similar to the way they are in the application described in this dissertation.

\subsection{Personal User Experience}
\label{subsec:personalexperience}
\input{chap6/PersonalExperience.tex}

\subsection{Project Evaluation}
Overall, the project went well. The project goal was to create a proof-of-concept of an instruction application using Google Glass, as well as to evaluate Google Glass in terms of the user experience. These goals have been reached  without any major setbacks. 

More difficult aspect of the project included understanding the Google Glass example application, BarcodeEye, as the application in some ways covered more than what the proof-of-concept application was meant to cover. For instance, BarcodeEye handled ISBN, which was not needed in this project. If redone, the BarcodeEye code could have been better refactored along the way, where unnecessary code would have been removed as soon as such code was deemed unnecessary. Doing so might have compressed the code somewhat and also made changes easier to implement. 

Being able to update an image on a slide also proved difficult, as the slides were to be loaded in faster than the images could be loaded in on the slides, and as such the user either had to wait for the application or only have a default image instead of the intended one. This was first solved by passing the \texttt{ImageView}, which contained the image, around, which is normally not good praxis as you rather want to pass the object going inside the view around as argument instead.

Through code review and evaluation the issue was solved by implementing a listener on the specific slide containing an image, such that when the image was loaded the method implemented through the listener was called, and the slide updated with the loaded image.

The project was developed through sprints, lasting two weeks each, with a sprint demonstration at the end of each sprint. The sprint demonstration consisted of a demonstration the work done so far to the supervisor, making sure the project was still on the right track and that the development was not falling behind schedule.

\subsection{Back-End Conclusions}
The dissertation involving the back-end part of the project, written by Richard Hoorn, concludes that while Google Glass is an impressive piece of technology, Google Glass was still outperformed by smartphones since Google Glass is not able to handle larger data sizes. Data sizes above one megabyte were very difficult or even impossible for Google Glass to handle.

A possible solution would be to not let Google Glass do all the work, but rather connect Google Glass to a smartphone, from which information is then streamed. As such, Google Glass would simply act as a display, displaying the information sent from the smartphone, and would not have to handle all of the downloaded information at the same time.

Hoorn also discussed the possibilities of headaches which Google Glass could cause and the fact that looking up at the screen could cause eye strain. These concerns have been adressed by Google, who states that Google Glass is not meant for usage of longer periods of time. Using Google Glass longer periods of time will also cause them to overheat, causing both performance issue as well as a very hot exterior. As such, Google Glass is perhaps not suited for industry use, where Google Glass would potentially be used over longer periods of time, but is rather suited and designed for the more casual user.

\subsection{Future Work}
\label{subsec:futurework}
\input{chap6/FutureWork.tex}

\subsection{Concluding Remarks}
Google Glass is an interesting attempt at developing technology further. The potential of Google Glass is exciting. However, the fact that Google Glass is intended for use in short bursts, simply to take a picture or to send a message, makes it hard to argue in favour of using Google Glass in any situation apart from more casual ones. As long as any work done on the device is not too complex or demanding in terms of hardware, Google Glass can be very helpful.

However, Google Glass should not be seen as a competitor to smartphones, but rather a complementary device which may be used together with a smartphone. In terms of displaying instructions to a user, who is assembling components, Google Glass could be useful as the user does not have to shift focus and look away. As long as the instructions are short, simple and do not take up too much data space, Google Glass would be the preferred device over smartphones.

However, the smartphone's bigger screen and stronger hardware make smartphones the preferred choice when the instructions are complex and contain, for instance, a video, as the video's data size potentially would be too large for Google Glass to handle without performance issues.

One solution would be to compress the video, both in length and data size, or to have the video stream from a smartphone on to Google Glass, using Google Glass and a smartphone as complements to each other. As Google continues to develop Google Glass behind closed doors, it will be interesting to see how Google Glass has evolved once it is shown again. Until such time, one can only hope Google keeps improving on Google Glass, and relaxes of some of their restrictions, as Google Glass, despite its flaws, shows great potential.