%% Sample dissertation using the kau_report LaTeX class
%%
%% 950203  Michael Kelsey -- LaTeX2e format (cit_thesis)
%% 990210  Anna Brunstrom -- Modified to KAU requirements
%% 990420  Anna Brunstrom -- Copyright page added + some minor updates

%\documentclass{kaumasters}
\documentclass[12pt,twoside]{kau_report}

\usepackage{float}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{url}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{color}
\usepackage{pdfpages}
\usepackage{mathtools}
\usepackage{chngcntr}
%\usepackage{refcheck}

\AtBeginDocument{\counterwithin{lstlisting}{section}}

\setlength{\fboxsep}{0pt}

\definecolor{dkgreen}{rgb}{0, 0.6, 0}
\definecolor{gray}{rgb}{0.5, 0.5, 0.5}
\definecolor{mauve}{rgb}{0.58, 0, 0.82}
\lstset
{
	frame=tb,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=left,
	numberstyle=\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}

% If you write in Swedish, uncomment line below
%\usepackage{swedish}

% Define the parameters in the preamble

\title{An Evaluation of Google Glass\\ 
\large Design, Implementation and Evaluation of an Instruction Application for Google Glass and Smartphones}

\pubnum{June, 2015}

\author{Johan H\"{a}ger}

\date{2015-06-05}

\advisor{Donald F. Ross}
\examiner{Thijs. J. Holleboom}

% The actual document starts here
\begin{document}


% Create the title page. If you write in swedish use the second
% line below instead.
\makekautitle
%\makeswekautitle

%% Create the copyright page. If you write in swedish use the second
% line below instead.
\copyrightpage
%\swecopyrightpage

 %Start roman numbering
\begin{frontmatter}

% Create approval page. select the appropriate command depending
% on how many authors you have. If you write in swedish use 
% one of the sweapproved lines below instead.
%\approved
\approved
%\approvedthree{Author One}{Author Two}{Author Three}
%\sweapproved
%\sweapprovedtwo{Author One}{Author Two}
%\sweapprovedthree{Author One}{Author Two}{Author Three}

% Create abstract 
\begin{abstract}
Assembling components in a production line could potentially be a tedious task, and done by the books, step-by-step. However, an employee who is constructing many different product may not know all the steps by heart. As such they will be reliant on an instruction manual. But an instruction manual must be carried around and lied down. Instead new technology might make the process more efficient. Google Glass puts a display slightly above the user's line of sight and can be controlled via voice commands, and as such solves many of the problems with carrying around instruction manuals. This dissertation is an evaluation of Google Glass and describes the design, implementation and evaluation of an instruction application for both Google Glass and smartphones. The smartphone version was done in order to provide a reference point as well as a method of comparison with the Google Glass application. Testing was done on the different steps of the application, from the QR code has been scanned until the information is being displayed to the user. The results show that Google Glass is almost always about half a second slower, in all steps, compared to smartphone equivalents. The conclusion is that Google must upgrade and improve on, especially, the hardware of Google Glass. Google Glas overheats a lot and the camera is bad. Google's restrictions also limits what developers might be able to do with the device. However, Google Glass is easy to use and has potential to become a more useful device in the future.
\\
% KEYWORDS
\\
\textbf{Keywords:} Google Glass, Android
%Motivation:
%Why do we care about the problem and the results? If the problem isn't obviously "interesting" it might be better to put motivation first; but if your work is incremental progress on a problem that is widely recognized as important, then it is probably better to put the problem statement first to indicate which piece of the larger problem you are breaking off to work on. This section should include the importance of your work, the difficulty of the area, and the impact it might have if successful.
%Problem statement:
%What problem are you trying to solve? What is the scope of your work (a generalized approach, or for a specific situation)? Be careful not to use too much jargon. In some cases it is appropriate to put the problem statement before the motivation, but usually this only works if most readers already understand why the problem is important.
%Approach:
%How did you go about solving or making progress on the problem? Did you use simulation, analytic models, prototype construction, or analysis of field data for an actual product? What was the extent of your work (did you look at one application program or a hundred programs in twenty different programming languages?) What important variables did you control, ignore, or measure?
%Results:
%What's the answer? Specifically, most good computer architecture papers conclude that something is so many percent faster, cheaper, smaller, or otherwise better than something else. Put the result there, in numbers. Avoid vague, hand-waving results such as "very", "small", or "significant." If you must be vague, you are only given license to do so when you can talk about orders-of-magnitude improvement. There is a tension here in that you should not provide numbers that can be easily misinterpreted, but on the other hand you don't have room for all the caveats.
%Conclusions:
%What are the implications of your answer? Is it going to change the world (unlikely), be a significant "win", be a nice hack, or simply serve as a road sign indicating that this path is a waste of time (all of the previous results are useful). Are your results general, potentially generalizable, or specific to a particular case?

\end{abstract}
\cleardoublepage


% If you write in swedish you need a second abstract in 
% English. Uncomment lines below for the second absract.
%\renewcommand{\abstractname}{Your English Title}
%\begin{abstract}
%Put the text of your second abstract here
%\end{abstract}


% Create acknowledgements (optional part)
\begin{acknowledgements}
Mats Persson - handledare Sogeti sprintdemo

Donald F. Ross - handledare kau

Kalle Henriksson - kodgranskning

Daniel Johansson - utlåning av testequipment kau

Sogeti i allmänhet

A final thank you to everyone who have been supportive and wished me good luck throughout the process of working on this project as well as writing this dissertation.

todo - förklara vad glassware är och använd det istället för application igenom rapporten?

% If you want acknowledgements they go here 
\end{acknowledgements}
\cleardoublepage

% Set up contents, list of figures and list of tables
  \tableofcontents
  \cleardoublepage

  \listoffigures
  \cleardoublepage

  \listoftables
  \cleardoublepage
  
  \lstlistoflistings
  \cleardoublepage

\end{frontmatter}
% End of roman numbering

% Here comes the main body, it's your job to fill this in...
\section{Introduction}
\label{sec:introduction}
\input{Introduction.tex}
\cleardoublepage

\section{Background}
\label{sec:background}
\input{Background.tex}
\cleardoublepage

\section{Design}
\label{sec:design}
\input{Design.tex}
\cleardoublepage

\section{Implementation}
\label{sec:implementation}
\input{Implementation.tex}
\cleardoublepage

\section{Results} % Result / Evaluation
\label{sec:resultevaluation}
\input{ResultEvaluation.tex}
\cleardoublepage

\section{Conclusions}
\label{sec:conclusion}
\input{Conclusion.tex}
\cleardoublepage

%\nocite{*}

% Start of reference section. 
\begin{singlespace}
\bibliography{myBibliography}
\bibliographystyle{plain}
\end{singlespace}
\cleardoublepage

% Appendix if present goes here (optional part)
\appendix
\section{Abbreviations}
\label{sec:abbreviations}
\input{abbreviations.tex}
\cleardoublepage

\section{Results}
\label{app:results}
\input{tables/DistanceTable.tex}
\input{tables/ComplexityTable.tex}
\input{tables/displayTable.tex}
\cleardoublepage

%\section{Voice Command Checklist}
%\label{app:voiceCommandChecklist}
%\input{voiceCommandCheckTableUnchecked.tex}
%\cleardoublepage


\section{Code}
\label{app:code}
\input{Code.tex}
\cleardoublepage

\section{Project Specification (In Swedish)}
\label{app:projectspec}
\includepdfmerge{Google_Glass.pdf,-}

\end{document}
