The Google Glass application gives users the option to use voice commands in order to navigate the slides. The user opens the voice command menu by saying ``ok glass'' at any point in the application when ``ok glass'' is shown at the bottom of the screen. The voice command feature is available at all times except when the camera is active. In other words the voice commands are unavailable when the application is waiting to scan a QR code.

The voice command menu contains the following options.

\begin{itemize}
	\item \textbf{Show next slide}
	
	The application scrolls to the next slide. If the current slide is the last slide, and in other words no other slides are following, the application does nothing.
	\item \textbf{Show previous slide}
	
	The application scrolls to the previous slide. If the current slide is the first slide, and in other words no other slides comes before the current slide, the application does nothing.
	\item \textbf{Show components}
	
	The application scrolls to the first slide showing information on a component. If the user is currently on the first slide showing information on a component the application does nothing. 
	\item \textbf{Show instructions}
	
	The application scrolls to the first slide showing an instruction. If the user is currently on the first slide showing an instruction the application does nothing.
	\item \textbf{Scan again}
	
	The application launches the camera and expects the user to scan another QR code.
\end{itemize}

Implementing voice command in the Google Glass application is done by following Google's step-by-step guide on how to implement voice commands in Google Glass applications~\cite{howToVoiceInput}. Listing~\ref{voiceCommandXML} shows the XML written according to Google's step-by-step guide, which gives the voice commands used in the application. Using contextual voice commands according to Google's step-by-step guide means that ``ok glass'' is displayed at the bottom of the screen at all times when voice commands are available. ``ok glass'' also comes with a dark overlay, seen for instance in Figure~\ref{fig:cardLayout}, which is transparent yet darkens the slides, especially near the bottom of the slides where ``ok glass'' is shown. Although the dark overlay could potentially distort the slides a bit, especially when the slide contains only an image and no text, alter the ``ok glass'' overlay in any way is not possible~\cite{voiceCommandCustom1, voiceCommandCustom2}. The dark overlay does however ensure that ``ok glass'' is always visible, no matter what the background image look like.

Although none of the voice commands has been sent in for official approval by Google most of the voice commands follow the design guidelines provided by Google~\cite{glassVoiceChecklist}. As seen in Table~\ref{tab:voiceCommandCheckTableChecked} 11 of the 15 voice command guidelines provided by Google have been followed. However, some of the guidelines have been applied to some or most of the voice command used within the application, but not all. For instance ``Show components'' does not follow the first guideline of the voice command checklist. However, the ``Show components'' voice command remains a part of the application as ``Show components'' is a key feature of the application.

\begin{lstlisting}[language=XML, caption={The voice command menu XML file}, label=voiceCommandXML]
<menu xmlns:android="http://schemas.android.com/apk/res/android">
	<item
		android:id="@+id/next_menu_item"
		android:title="Show next slide" >
	</item>
	<item
		android:id="@+id/previous_menu_item"
		android:title="Show previous slide" >
	</item>
	<item
		android:id="@+id/components_menu_item"
		android:title="Show components" >
	</item>
	<item
		android:id="@+id/instructions_menu_item"
		android:title="Show instructions" >
	</item>
	<item
		android:id="@+id/scan_menu_item"
		android:title="Scan again" >
	</item>
</menu>
\end{lstlisting}

\input{voiceCommandCheckTableChecked}

The reason for not following guidelines 11--14 is because they would make the voice commands longer. As the voice commands may potentially be said often while using the application, as the user may proceed through the slides quite fast, shorter voice commands make for more comfortable use. As the voice commands still follow guideline 6 the voice commands were deemed to be long enough to still ensure high recognition quality.